Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-28 TACAS2018/paper.tex
sec 7

In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS~\cite{DBLP:conf/asplos/2006}. Broadly speaking, CEGIS
denotes an iterative technique where each step performs inductive
generalisation based on counterexamples provided by a verification
engine. In each iteration, an inductive synthesiser produces a
candidate solution that obeys the specification for a limited number
of inputs. Subsequently, this candidate is passed to a verification
oracle that checks it against the specification for all possible
inputs. If the verification fails, then the witness counterexample is
passed back to the synthesis phase, where it is added to the set of
inputs to be considered in the next loop iteration. Otherwise, the process terminates.

%
We enhance the standard CEGIS architecture %\cite{abate2017automated}
with an abstraction-refinement approach and with optimization,
resulting in the novel CEGIS-OR (CEGIS with Optimization and
Refinement).  By using abstraction refinement, CEGIS-OR tackles the
scalability issues inherent in program synthesis as it allows using
potentially coarse abstractions of the given model that are only
refined on demand.  Since the use of coarse abstractions may result in
low-quality candidate solutions (i.e. candidates that fail the
specification on a very large number of inputs), after each synthesis
phase we use optimization techniques to improve the produced
candidates.  In particular, our optimization procedure aims at
reducing the size of the reach space of the closed loop system, while
maintaining other dynamical properties (safety, stability, and
response time).

@@

If we cannot optimize the candidate  we signal the {\sc Abstract} phase to 
use the updated $\phi_\mathit{synth}$ and request {\sc Synthesise} to produce a new
candidate.  Otherwise the optimized candidate solution is given back to
{\sc Verify Synthesis}.

>>>>

In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS. Broadly speaking, CEGIS
denotes an iterative technique where each step performs inductive
generalisation based on counterexamples provided by a verification
engine. In each iteration, an inductive synthesiser produces a
candidate solution that obeys the specification for a limited number
of inputs. Subsequently, this candidate is passed to a verification
oracle that checks it against the specification for all possible
inputs. If the verification fails, then the witness counterexample is
passed back to the synthesis phase, where it is added to the set of
inputs to be considered in the next loop iteration. Otherwise, the process terminates.

%
We enhance the standard CEGIS architecture 
with an abstraction-refinement approach and with optimization,
resulting in the novel CEGIS-OR (CEGIS with Optimization and
Refinement).  By using abstraction refinement, CEGIS-OR tackles the
scalability issues inherent in program synthesis as it allows using
potentially coarse abstractions of the given model that are only
refined on demand.  Since the use of coarse abstractions may result in
low-quality candidate solutions (i.e. candidates that fail the
specification on a very large number of inputs), after each synthesis
phase we use optimization techniques to improve the produced
candidates.  In particular, our optimization procedure aims at
reducing the size of the reach space of the closed loop system, while
maintaining other dynamical properties (safety, stability, and
response time).

@@

If we cannot optimize the candidate  we signal the {\sc Abstract} phase to 
use the updated $\phi$ and request {\sc Synthesise} to produce a new
candidate.  Otherwise the optimized candidate solution is given back to
{\sc Verify Synthesis}.
